Vector Similarity based Entity Linking

### 2015-07-09 paper.tex
added Christina

\author{Felix Tristram \and Sebastian Walter \and Philipp Cimiano}
\authorrunning{Felix Tristram \and Sebastian Walter \and Philipp Cimiano}
% (feature abused for this document to repeat the title also on left hand pages)

>>>>

\author{Felix Tristram \and Christina Unger \and Sebastian Walter \and Philipp Cimiano}
\authorrunning{Felix Tristram \and Christina Unger \and Sebastian Walter \and Philipp Cimiano}
% (feature abused for this document to repeat the title also on left hand pages)
